Developing Software Center Using Evolutionary Prototyping Based-on HTML5

### 2014-05-06 Latex/Paper_format.tex
review

YaST (Yet another Setup Tool)
Software center for openSUSE. It use to manage all of user need for use openSUSE. Example to install application, package, network setting etc. YaST use ruby and YCP for language programming and Qt for user interface[2].

Ubuntu Software Center\\Software management for Ubuntu by Canonical. It is free software written in Python, PyGTK/PyGObject based on GTK+ and the further development of the GNOME application, gnome-app-install.[3][4]

@@

WarSi design base on HTML5, AngularJS for front-end. Back-end use Vala programming. Vala chosen because it can communicate with operating system like run specific apt command use Vala API. Another reason Vala can run simultanly with Manokwari Desktop base on GNOME 3.

Figure 3 show how design of WarSi.

@@

\subsubsection{Use Case Diagram}
Figure 5 show the use case diagram for software center.

@@

\subsubsection{Activity Diagram}
Figure 6 show activity diagram generally.

@@

@@

Activity Diagram Search Applications. Figure 7 is an activity diagram for a search application. Search Application is divided into two, namely by entering a keyword in the search field and the search for applications by category. Process for Figure 7 are:
\begin{itemize}
\item Users select search for applications by name or by category of applications,
\item If you select by name, users enter a keyword or the name of the application you are looking for in the search field to find the application,
\item If you select a category based application, the user selects a category that existed until the application is found,
\item Application is found, the user chose to install/remove or update the application,
\item Installation process, and the process is complete.
\end{itemize}

Activity Diagram Repository Management. Process for Figure 8 are:
\begin{itemize}
\item User select a menu from the main menu next repository, system will display the page repository, there are two options, choose source repository or directly perform the update,
\item User can make changes to the repository by selecting the list
repository that is already available,
\item When the user makes changes to the repository, the system will saved the changes,
\item When the user performs an update to the update repository the repository will be made and the system will display the process update,
\item After update user can upgrade system if available, then the system will display the process upgrade.
\item Process is completed.
\end{itemize}

@@

\subsubsection{Sequence Diagram}
Figure 9 show sequence diagram for search application by name.

@@

\subsection{Result Development}
After development finished, the result is prototype software center for BlankOn Linux. Base on HTML5 for front-end. Screenshoot WarSi can be found in Figure 12 and Figure 13.

Figure 14 show page to search application.
\begin{figure}[!t]
\centering
\includegraphics[scale=0.31]{image/03HamalanPencarian.png}
\caption{Implement Search Page}
\end{figure}

Figure 15 show page repository management.
\begin{figure}[!t]
\centering
\includegraphics[scale=0.31]{image/02HalamanRepository.png}
\caption{Implement Repository Management}
\end{figure}

@@

Under the terms of usability testing software center, it is concluded that the majority of respondents are satisfied with the application made. Data usability test results that the respondents strongly agreed by 80\%, 20\% agree, neutral 0\%, which is expressed as 0\% disagree and strongly disagree that states as much as 0\%. Based on these test results, it can be concluded that the software center that has made this feasible for use. However, the need for further development of the application to obtain optimal application. Figure 15 and Figure 16 show percent of functionally and satisfied user using WarSi.

>>>>

YaST (Yet another Setup Tool), software center for openSUSE. It use to manage all of user need for use openSUSE. Example to install application, package, network setting etc. YaST use ruby and YCP for language programming and Qt for user interface[2].

Ubuntu Software Center, software management for Ubuntu by Canonical. It is free software written in Python, PyGTK/PyGObject based on GTK+ and the further development of the GNOME application, gnome-app-install.[3][4]

@@

WarSi design base on HTML5, AngularJS for front-end. Back-end use Vala programming. Vala chosen because it can communicate with operating system like run specific apt command use Vala API. Another reason Vala can run simultanly with Manokwari Desktop base on GNOME 3. Figure 3 show how design of WarSi.

@@

\subsubsection{Use Case Diagram}
Use case is a construction diagram to describe the relationships that occur between actors with the activities contained in the system. Target modelling use case include defining the functional and operational needs of the system by defining usage scenarios that the system will be built. From the analysis of existing applications that use case diagram for the Software Center application can be seen in Figure 5.

@@

\subsubsection{Activity Diagram}
Activity diagram is used to model processes that occur in the system which would explain the activity on any existing functionality. Activity diagram can generally be seen in Figure 6.

@@

Figure 7 is an activity diagram for a search page application. Search Application is divided into two, namely by entering a keyword in the search field and the search for applications by category. Process for Figure 7 are:
\begin{itemize}
\item Users select search for applications by name or by category of applications,
\item If you select by name, users enter a keyword or the name of the application you are looking for in the search field to find the application,
\item If you select a category based application, the user selects a category that existed until the application is found,
\item Application is found, the user chose to install/remove or update the application,
\item Installation process, and the process is complete.
\end{itemize}

@@

Figure 8 is an activity diagram management repository. Users can choose the appropriate repository existing list. Process for Figure 8 are:
\begin{itemize}
\item User select a menu from the main menu next repository, system will display the page repository, there are two options, choose source repository or directly perform the update,
\item User can make changes to the repository by selecting the list
repository that is already available,
\item When the user makes changes to the repository, the system will saved the changes,
\item When the user performs an update to the update repository the repository will be made and the system will display the process update,
\item After update user can upgrade system if available, then the system will display the process upgrade.
\item Process is completed.
\end{itemize}

@@

\subsubsection{Sequence Diagram}
Sequence diagram illustrates the scenario and series of steps performed on the system in response to an event to produce a given output. Figure 9 show sequence diagram for search application by name. Figure 10 show sequence diagram for search application by category. Activity diagram for management repository show in Figure 11.

@@

\subsection{Result Development}
After development finished, the result is prototype software center for BlankOn Linux. Base on HTML5 for front-end. Screenshot WarSi can be found in Figure 12 and Figure 13.
\begin{figure}[!t]
\centering
\includegraphics[scale=0.31]{image/03HamalanPencarian.png}
\caption{Implement Search Page}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[scale=0.31]{image/02HalamanRepository.png}
\caption{Implement Repository Management}
\end{figure}

@@

Under the terms of usability testing software center, it is concluded that the majority of respondents are satisfied with the application made. Data usability test results that the respondents strongly agreed by 80\%, 20\% agree, neutral 0\%, which is expressed as 0\% disagree and strongly disagree that states as much as 0\%. Based on these test results, it can be concluded that the software center that has made this feasible for use. However, the need for further development of the application to obtain optimal application. Figure 14 and Figure 15 show percent of functionally and satisfied user using WarSi.
